|

### 2021-02-23 appendix/appendix.Rmd
version 0.1

Again, both players are *ex-ante* similar in terms of their expected utilities. This allow us to solve for the Symmetric Nash Equilibrium, where:

@@

We posted a Facebook ad in the municipality participating in the intervention. The ad invited potential participants to join the research and explained the payment scheme. If they clicked on the ad, they were directed to a Google Form, where they added their e-mail address and contact information.

@@

We use two primary datasets in the paper. First, we collected productivity data from the cell phones used by the participants in the field. Second, we collected governmental data on *A. aegypti*-borne diseases from the Brazilian Ministry of Health diseases notification system (SINAN).

@@

### Method of Delivery

@@

Replication materials are available at https://github.com/danilofreire/incentives-health-care.

>>>>

Again, both players are *ex-ante* similar in terms of their expected utilities. This allows us to solve for the Symmetric Nash Equilibrium, where:

@@

We posted a Facebook ad in the municipality participating in the intervention. The ad invited potential participants to join the research and explained the payment scheme. If they clicked on the ad, they were directed to a Google Form, where they added their email address and contact information.

@@

We use two primary datasets in the paper. First, we collected productivity data from the cell phones used by the participants in the field. Second, we collected governmental data on *A. aegypti*-borne diseases from the National Health Notification System (SINAN).

@@

### Delivery Methods

@@

Replication materials are available at https://github.com/danilofreire/incentives-healthcare.
